Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-06-28 paper/Analisis.tex
A Better Plots
updated in latex

The first quantitative conclusion of the effect of rotation in the
\ly line is that double peaks broaden and reduce their intensity,
while the line center rises. This procudes the impresion that, as the
rotational velocity increases, the double peaks are merged into a
single broad emission peak. This is msot evident in the highest
rotational velocities for the homogeneously distributed sources
(right panel in Fig.~\ref{fig:differentvelocities}).

@@

\begin{figure*}
     \includegraphics[width=0.45\textwidth]{2dHistogram0t5HOM.png}
     \includegraphics[width=0.45\textwidth]{2dHistogram300t5HOM.png}    \\
     \includegraphics[width=0.45\textwidth]{2dHistogram0t5.png}
     \includegraphics[width=0.45\textwidth]{2dHistogram300t5.png}

@@

In order to gain a deeper understanding of these results we 2D
histograms for the number of scaterrings as a function of the outgoing
dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
the results of such histogram in the case $\tau{\rm H}=10^5$ for the
static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
results for the homogeneous (central) source distribution. The color
scale is logarithmic in the number of photons at a certain value
$x-N_{\rm scatt}$. This Figure clearly support our hypothesis about
the photosphere in the homogeneous distribution, in this case most of
the photons that left with $x\sim 0$ have escaped with less than $10$
scatterings, clearly explaining the origin of a single central
peak. However, for a central distribution the situation is
different. In this case the number of scatterings remains high, on the
order of the optical depth, but the two peaks do get closer to each
other. In this situation each scattering leaves the photon closer to
the center of the line than the static case.

@@

If there is a change in the number of scatterings with rotational
velocity, there must be a change in the probability of being absorbed
if dust is present. We study how rotation impacts the escape fraction
of \ly photons.

Taking into account the results in the previous section, we do not expect any
change in the case of central distributions given that the average
number of scatterings remain constant. On the other hand, in the
homogeneous distribution there is a considerable drop in the number of
scatterings as $V_{\rm max}$ increases, this preconditions the escape
fraction to increase as well.

Figure \ref{fig:efvsv} shows the dependence of the escape fraction as
a function of rotational velocity. This Figure illustrates how our
reasoning in the previous paragraph is correct. The escape fraction
barely changes for the central source distribution, while it rises
as the velocity $V_{\rm max}$ increases for the homogeneous case. The
velocity has a higher relative impact in the models with low optical
depth $\tau_{\rm H}=10^5$,$10^{6}$, where it can raise from $xxx$ in
the static case up to $xxx$ at $V_{\rm rot}=300$\kms.

>>>>

The first quantitative conclusion of the effect of rotation in the
\ly line is that double peaks broaden and reduce their intensity
while the line center rises. This produces the impresion that, as the
rotational velocity increases, the double peaks are merged into a
single broad emission peak. This is msot evident in the highest
rotational velocities for the homogeneously distributed sources
(right panel in Fig.~\ref{fig:differentvelocities}).

@@

\begin{figure*}
     \includegraphics[width=0.45\textwidth]{2dHistogram0t5HOM.png}
     \includegraphics[width=0.45\textwidth]{2dHistogram300t5HOM.png} 
     \includegraphics[width=0.45\textwidth]{2dHistogram0t5.png}
     \includegraphics[width=0.45\textwidth]{2dHistogram300t5.png}

@@

In order to gain a deeper understanding of these results we prepare 2D
histograms for the number of scaterrings as a function of the outgoing
dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
the results of such histogram in the case $\tau{\rm H}=10^5$ for the
static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
results for the homogeneous (central) source distribution. The color
scale is logarithmic in the number of photons at a certain value
$x-N_{\rm scatt}$. This Figure clearly support our hypothesis about
the photosphere in the homogeneous distribution, in this case most of
the photons that left with $x\sim 0$ have escaped with less than $10$
scatterings, clearly explaining the origin of a single central
peak. However, for a central distribution the situation is
different. In this case the number of scatterings remains high, on the
order of the optical depth, but the two peaks do get closer to each
other. In this situation each scattering leaves the photon closer to
the center of the line than the static case.

@@

We also study a dusty cloud configuration to measure the effect of
rotation on the escape fraction. We expect that the modified number of
scatterings to be reflected in this amount of photons aborbed by
dust. Following this line of thought,  we do not expect any change in
for a dusty cloud with central source of radiation given that the
number of scatterings remains close to constant. On the other hand, in
the case of an homogenous radiation source the number of scatterings
drops as $V_{\rm max}$ increases, which might be reflected as an
increasing escape farction.

%If there is a change in the number of scatterings with rotational
%velocity, there must be a change in the probability of being absorbed
%if dust is present. We study how rotation impacts the escape fraction
%of \ly photons.

%Taking into account the results in the previous section, we do not expect any
%change in the case of central distributions given that the average
%number of scatterings remain constant. On the other hand, in the
%homogeneous distribution there is a considerable drop in the number of
%scatterings as $V_{\rm max}$ increases, this preconditions the escape
%fraction to increase as well.

Figure \ref{fig:efvsv} shows the dependence of the escape fraction as
a function of the maximum rotational velocity, confirming that our
intuitions in this respect is correct. For the central source
distribution the escape fraction barely shows any change, while for
the homogeneous case there is a clear rise in the escape fraction for
high rotational velocities.  Rotation has a higher relative impact in
the models with low optical depth $\tau_{\rm H}=10^5$,$10^{6}$, where
it can raise from $xxx$ in the static case up to $xxx$ at $V_{\rm
  rot}=300$\kms.

%This Figure illustrates how our
%reasoning in the previous paragraph is correct. 
%The escape fraction
%barely changes for the central source distribution, while it rises
%as the velocity $V_{\rm max}$ increases for the homogeneous case.
